\documentclass{SSBT-BE}
\usepackage{makeidx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{%
  babel,
  algorithmic,
  algorithm,
  caption
}

\usepackage{url}
\usepackage[breaklinks=true]{hyperref}

\usepackage[intoc]{nomencl}
\renewcommand{\nomname}{Abbreviations}
\makenomenclature
\usepackage{imakeidx}
\makeindex

\begin{document}

\title{House Price Prediction Using Machine Learning}
\author{Janhavi Kailas Chaudhari \\ Anup Sanjay Patil \\ Mayur Manohar Patil \\ Bhushan Ramkrushna Upasani \\ Priyakumari Kailassing Rajput }

\dept{Department of Computer Engineering}
\supervisor{Miss. Priti Sharma}
\submitdate{2020 - 2021}
\degree{Bachelor of Engineering}
\specialization{Computer Engineering}
\type{Project}
%\type{Seminar}
\hod{Prof. Dr. Girish K. Patnaik}

\beforepreface


\prefacesection{Acknowledgements}
%\input{acknowledgement}
We take the opportunity to express our gratitude to all those who have rendered co-operation
and guidance that supported us while analyzing and developing the design of this project
right from beginning up till now.
First of all we would like to express our deepest appreciation toward Dr. Girish K. Patnaik
(H.O.D. of Computer Engineering) and Miss. Priti Sharma (Guide) whose valuable guidance
supported us in completing the analysis and designing of our final year project. We would also like to
thank and express our respect and gratitude to Dr. K. S. Wani (Principal) for providing
us this opportunity.
Last but not least we are profoundly grateful and obliged to Miss. Priti Sharma, for her guidance, motivation and continuous encouragement throughout to see that
whole process is right on its target since its commencement.


\acknowledgeauthor



% Use following command at the command prompt to display the Abbreviations
% makeindex thesis.nlo -s nomencl.ist -o thesis.nls
\newpage
% \addcontentsline{toc}{chapter}{List of Abbreviations}
% \printnomenclature


\newpage
\afterpreface
\listoftables
\listoffigures
%\input{glossary}
\clearpage
\pagenumbering{arabic}
\pagestyle{plain}


\prefacesection{Abstract}
Machine learning plays a major role from past years in image detection, spam reorganization, normal speech command, product recommendation and medical diagnosis.
Present machine learning algorithm helps in enhancing security alerts, ensuring public safety and improve medical enhancements. Machine learning system also provides
better customer service and safer automobile systems.\\
Designing an effective machine learning model for prediction of regression and classification problem is a tedious endeavor. Significant time and expertise are needed to
customize the model for a specific problem. A significant way to reduce the complicated design is by using Automated Machine Learning (AML) that can intelligently
optimize the best pipeline suitable for a problem or dataset. This study utilizes machine learning algorithms as a research method that develops housing price prediction
models. In that point a housing cost prediction model to support a house vendor or a
real estate agent for better information based on the valuation of house is recommended.

% \chapter{Introduction}
% \input{./introduction/introduction}

% \chapter{LaTex Basic Blocks}
% \input{./trust/gkp}

% %\chapter{Key Management}
% \label{CH-Key Management}
% %\input{./key/gkp}

% \chapter{Conclusion and Future Work}
% %\input{conclusion}
% \appendix
% %\input{appendix}

% \chapter{Disasters in India}
% %\input{./appendix_disaster}





%......Main Project report starts form here......

\chapter{Introduction}
\input{Introduction/introduction}

\chapter{Project Planning and Management}
\input{Project Planning and Management/Project_Planning_and_Management}

\chapter{Analysis}
\input{Analysis/analysis}

\chapter{System Design}
\input{System Design/system_design}

\chapter{Conclusion and Future Work}
\input{Conclusion and Future Work/conclusion}



\printindex

\end{document}
